Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-05-19 2016_ICML/cmrs.tex
Changing conclusion to be more diplomatic about ES
Adding knowledge gradient to background

The second class of acquisition functions are \emph{improvement-based policies}, such as the probability of improvement \citep[PI,][]{kushner_new_1964} over the current best value, which can be calculated in closed-form for a GP model:
$$a_{PI}(\mathbf{x}; \mathcal{D}_n) := \mathbb{P}[f(\mathbf{x}) > \tau] = \Phi(\gamma(\mathbf{x})),$$
where $\gamma(x) = (\mu_n(\mathbf{x}) - \tau) / \sigma_n(x)$, $\Phi(\cdot)$ denotes the cumulative distribution function of the
standard Gaussian, and $\tau$ denotes the incumbent, typically the best function value observed so far: $\tau = \max y_i$.
Since PI is known to exploit quite aggressively \cite{jones_taxonomy_2001}, a more popular
alternative is the \emph{expected improvement} \citep[EI,][]{mockus_application_1978} over the
current best value, which can again be computed in closed form for a GP model:
\begin{equation*}
\begin{split}
 a_{EI}(\mathbf{x}; \mathcal{D})
  & := \mathbb{E}[(f(x) - \tau)\mathbb{I}(f(x) > \tau)] \\
  &  = \sigma_n(\mathbf{x})\left(\gamma(\mathbf{x})\Phi(\gamma(\mathbf{x})) + \phi(\gamma(\mathbf{x}))\right),
\end{split}
\end{equation*}
where $\phi(\cdot)$ denotes the standard Gaussian density function.

@@

We have proposed MRS, a new class of acquisition functions for single- and multi-task
Bayesian optimization that is based on the principle of minimizing the expected
regret. We have compared MRS empirically to other acquisition functions on a
synthetic single-task optimization problem and a simulated multi-task robotic
control problem.  The results indicate that MRS performs favorably compared to the
other approaches and incurs less often a high regret than ES since its
objective is explicitly focused on minimizing the regret. An empirical
comparison with PES remains future work; since PES uses the same objective as ES
(minimizing $H(\mathbf{x}^\star)$), it will likely show the same deficit of
ignoring areas that have small probability $p^\star$ but could nevertheless cause a large
potential regret. On the other hand, PES allows a formal treatment
of GP hyperparameters and can be approximated more efficiently than ES or MRS.
Potential future research on approaches for addressing
GP hyperparameters and more efficient approximation techniques for MRS would thus be desirable. Additionally,
combining MRS with active learning as done for entropy search by
\citet{metzen_active_2015} would be interesting. Moreover, we consider MRS to
be a valuable addition to the set of base strategies in a portfolio-based BO
approach \cite{shahriari_entropy_2014}. On a more theoretical level, it would be interesting if formal regret bounds can be proven for MRS.

>>>>

The second class of acquisition functions are \emph{improvement-based policies}, such as the probability of improvement \citep[PI,][]{kushner_new_1964} over the current best value, which can be calculated in closed-form for a GP model:
$$a_{PI}(\mathbf{x}; \mathcal{D}_n) := \mathbb{P}[f(\mathbf{x}) > \tau] = \Phi(\gamma(\mathbf{x})),$$
where $\gamma(x) = (\mu_n(\mathbf{x}) - \tau) / \sigma_n(x)$, $\Phi(\cdot)$ denotes the cumulative distribution function of the
standard Gaussian, and $\tau$ denotes the incumbent, typically the best function value observed so far: $\tau = \max y_i$.
Since PI is known to exploit quite aggressively \cite{jones_taxonomy_2001}, a more popular
alternative is the \emph{expected improvement} \citep[EI,][]{mockus_application_1978} over the
current best value, which can again be computed in closed form for a GP model:
\begin{equation*}
\begin{split}
 a_{EI}(\mathbf{x}; \mathcal{D})
  & := \mathbb{E}[(f(x) - \tau)\mathbb{I}(f(x) > \tau)] \\
  &  = \sigma_n(\mathbf{x})\left(\gamma(\mathbf{x})\Phi(\gamma(\mathbf{x})) + \phi(\gamma(\mathbf{x}))\right),
\end{split}
\end{equation*}
where $\phi(\cdot)$ denotes the standard Gaussian density function.  A
generalization of EI is the \emph{knowledge gradient} factor \cite
{frazier_knowledge-gradient_2009}, which can better handle noisy observations,
which impede the estimation of the incumbent. The knowledge gradient requires
defining a set $A_n$ from which one would choose the final solution.

@@

We have proposed MRS, a new class of acquisition functions for single- and multi-task
Bayesian optimization that is based on the principle of minimizing the expected
regret. We have compared MRS empirically to other acquisition functions on a
synthetic single-task optimization problem and a simulated multi-task robotic
control problem.  The results indicate that MRS performs favorably compared to the
other approaches and incurs less often a high regret than ES since its
objective is explicitly focused on minimizing the regret. An empirical
comparison with PES remains future work; since PES uses the same objective as ES
(minimizing $H(\mathbf{x}^\star)$), it will likely show the same deficit of
ignoring areas that have small probability $p^\star$ but could nevertheless cause a large
potential regret. On the other hand, in contrast to ES and MRS, PES allows a formal treatment
of GP hyperparameters, which can make it more sample-efficient. Potential future research on approaches for addressing
GP hyperparameters and more efficient approximation techniques for MRS would thus be desirable. Additionally,
combining MRS with active learning as done for entropy search by
\citet{metzen_active_2015} would be interesting. Moreover, we consider MRS to
be a valuable addition to the set of base strategies in a portfolio-based BO
approach \cite{shahriari_entropy_2014}. On a more theoretical level, it would be interesting if formal regret bounds can be proven for MRS.
